---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# poc.occupational.insurance

<!-- badges: start -->
<!-- badges: end -->

The goal of poc.occupational.insurance is to give a proof of concept of a
3 state Markov Model to price classical insurance products for disability/occupational
insurance. A sample data set by the bank of St. Louis from 1977 is also included. 
This is a toy model, so if you want to stay solvent rather build on it 
instead of using it directly. Also it is a personal playground for using `R`.

## Installation

You can install the development version of poc.occupational.insurance like so:

``` r
# install.packages("devtools")
devtools::install_github("n-0/pococcupationalinsurance")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(poc.occupational.insurance)
## basic example code

```

